---
title: "02_clonal_diversity_analysis"
author: "Enric Vercher"
date: "2023-11-07"
output: html_document
---

```{r}
# load libraries
suppressPackageStartupMessages(library(airr))
suppressPackageStartupMessages(library(alakazam))
suppressPackageStartupMessages(library(data.table))
suppressPackageStartupMessages(library(dowser))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(scoper))
suppressPackageStartupMessages(library(shazam))
suppressPackageStartupMessages(library(tigger))
```

### Setting the clonal distance threshold with SHazaM


```{r}
m.44.s <- airr::read_rearrangement('C:/Users/d940401/Desktop/Analisis_immcantation/Analisis_Enric/Datos_Enric/Datos_TFM/00_Datos_filtrados_slurm/02_Genotipado/m.44_genotyped.tsv')
m.45.s <- airr::read_rearrangement('C:/Users/d940401/Desktop/Analisis_immcantation/Analisis_Enric/Datos_Enric/Datos_TFM/00_Datos_filtrados_slurm/02_Genotipado/m.45_genotyped.tsv')
m.48.s <- airr::read_rearrangement('C:/Users/d940401/Desktop/Analisis_immcantation/Analisis_Enric/Datos_Enric/Datos_TFM/00_Datos_filtrados_slurm/02_Genotipado/m.48_genotyped.tsv')
m.49.s <- airr::read_rearrangement('C:/Users/d940401/Desktop/Analisis_immcantation/Analisis_Enric/Datos_Enric/Datos_TFM/00_Datos_filtrados_slurm/02_Genotipado/m.49_genotyped.tsv')
m.50.s <- airr::read_rearrangement('C:/Users/d940401/Desktop/Analisis_immcantation/Analisis_Enric/Datos_Enric/Datos_TFM/00_Datos_filtrados_slurm/02_Genotipado/m.50_genotyped.tsv')
m.52.s <- airr::read_rearrangement('C:/Users/d940401/Desktop/Analisis_immcantation/Analisis_Enric/Datos_Enric/Datos_TFM/00_Datos_filtrados_slurm/02_Genotipado/m.52_genotyped.tsv')
```

## Altogether

The nearest-neighbor distance distribution is not always bimodal. In this case, if the data have multiple subjects, we can calculate the nearest neighbor distances across subjects to initialize the Gaussian fit parameters of the nearest-neighbor distance of inter (between) clones distribution. 

The nearest neighbor distances across subjects can be calculated by specifying the parameter `cross` in the function `distToNearest`. And then when we call function `findThreshold`, Gaussian fit parameters can be initialized by setting parameter `cross = dist_crossSubj$cross_dist_nearest`.

In the above data, there are 6 subjects. We will want to make make sure that the cross subject `distToNearest` values are valid. To calculate this do the following:

```{r}
m.44.s$subject <- "mouse_44"
m.45.s$subject <- "mouse_45"
m.48.s$subject <- "mouse_48"
m.49.s$subject <- "mouse_49"
m.50.s$subject <- "mouse_50"
m.52.s$subject <- "mouse_52"
```

```{r}
all_mice_analysis <- rbind(m.44.s, m.45.s, m.48.s, m.49.s, m.50.s, m.52.s)
```

```{r}
#son lo mismo
#Use genotyped V assignments, Hamming distance, and normalize by junction length
dist_nearest <- distToNearest(filter(all_mice_analysis, locus == "IGH"), nproc = 1,model="ham", normalize ="len",vCallColumn = "v_call_genotyped") #lo mismo que distToNearest(all_mice_analysis)
#dist_nearest <- distToNearest(all_mice_analysis,nproc = 1,model="ham", normalize ="len",vCallColumn = "v_call_genotyped")
# calculate cross subjects distribution of distance to nearest
dist_crossSubj <- distToNearest(filter(all_mice_analysis, locus == "IGH"), 
                                nproc = 1, cross = "subject")

# find threshold for cloning automatically and initialize the Gaussian fit parameters of the nearest-neighbor 
# distance of inter (between) clones using cross subjects distribution of distance to nearest
threshold_output <- findThreshold(dist_nearest$dist_nearest, 
                                  method = "gmm", model = "gamma-norm", 
                                  cross = dist_crossSubj$cross_dist_nearest,
                                  cutoff = "user", spc = 0.995)
threshold <- threshold_output@threshold
threshold
```
Este valor (0.05594973) es similar a la mediana del conjunto de los thresholds por ratón indivual.

# Plot de todos juntos

```{r}
plot(threshold_output, binwidth = 0.02, 
     cross = dist_crossSubj$cross_dist_nearest, silent = T) + 
  theme(axis.title = element_text(size = 18))
```

#Si los hago por separado y saco la media y mediana

```{r}
# Lista para almacenar los umbrales
thresholds <- c()

# Iteración para cada ratón
for (subject in c("mouse_45", "mouse_48", "mouse_49", "mouse_50", "mouse_52")) {
    # Cálculo del umbral para cada ratón
    dist_nearest <- distToNearest(dplyr::filter(all_mice_analysis, locus == "IGH", subject == subject))
    threshold_output <- findThreshold(dist_nearest$dist_nearest, method = "gmm", model = "gamma-norm", cutoff = "user", spc = 0.995)
    threshold <- threshold_output@threshold
    
    # Almacenar el umbral en la lista
    thresholds <- c(thresholds, threshold)
}

# Calcular la media y la mediana de los umbrales
mean_threshold <- mean(thresholds)
median_threshold <- median(thresholds)

# Mostrar los resultados
mean_threshold
median_threshold
```


# Si hacemos la asignación clonal con Scoper

```{r}
# call clones using hierarchicalClones
assigned_clone_scoper <- hierarchicalClones(all_mice_analysis,
                              cell_id = "cell_id",
                              threshold = 0.05594973,
                              only_heavy = TRUE, split_light = FALSE,
                              summarize_clones = FALSE)
```

Como hemos eliminado las cadenas ligeras, no las encuentra.

# Create germlines

```{r}
# read in IMGT files in the Docker container
references <- readIMGT(dir = "C:/Users/d940401/Desktop/Analisis_immcantation/Analisis_Enric/data_IMGT/germlines/imgt/mouse/vdj_scoper")
# reconstruct germlines
assigned_clone_scoper <- createGermlines(assigned_clone_scoper,references, nproc = 1)
```
Fallan 2 igual que al hacerlo con el creategermlines.py en el cluster.

```{r}
# this is typically only done on heavy chains, but can also be done on light chains
results_heavy <- dplyr::filter(assigned_clone_scoper, locus == "IGH")

# calculate SHM frequency in the V gene
data_mutation <- shazam::observedMutations(results_heavy,
                              sequenceColumn = "sequence_alignment",
                              germlineColumn = "germline_alignment_d_mask",
                              regionDefinition = IMGT_V,
                              frequency = TRUE,
                              combine = TRUE,
                              nproc = 1)
```

Salen iguales. Trabajaremos con el del cluster.







